|

### 2021-07-26 article/articleCustomerDropoutMembership.Rmd
upd

# A function to allow for showing some of the inline code
rinline <- function(code) {
  html <- '<code  class = "r">``` `r CODE` ```</code>'
  sub("CODE", code, html)

##https://opensource.com/article/19/5/python-3-default-mac
#Sys.setenv(RETICULATE_PYTHON = "C:/Users//AppData/Local/Microsoft/WindowsApps/python3")

#install.packages("reticulate")
#library(reticulate)
#virtualenv_create("artigosurvival",python_version="3.7.10")
#use_virtualenv("artigosurvival", required = TRUE)
}   
```

```{r RETICULATE,echo = FALSE}
#set environment first
Sys.setenv(RETICULATE_PYTHON="C:\\Users\\sobre\\anaconda3\\envs\\survival\\python.exe")
#call reticulate
library(reticulate)
#activate environment
use_condaenv("survival", required = TRUE)
#use_virtualenv("C:/Users/mangelo.EEG/Documents/python")
```

@@

```{r summarytable, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(gtsummary)
library(kableExtra)

tbl <- df_members %>%
    tbl_summary(statistic = list(all_continuous() ~ "{mean} ({sd})",
                                 all_categorical() ~ "{p}%")
               )
as_kable_extra(tbl,booktabs=T,caption="Summary statistics")
```

@@

correlation_matrix(df_members, figure_size=(10,10), text_fontsize=6)
```

The average age in our data is `r round(mean(df_members$age,na.rm = TRUE),1)`.

>>>>

# A function to allow for showing some of the inline code
rinline <- function(code) {
  html <- '<code  class = "r">``` `r CODE` ```</code>'
  sub("CODE", code, html)
}   
```

```{r RETICULATE,echo = FALSE}
#Replace by your environment, usually which python solves the problem
#conda env list also is a good option
#set environment first
switch(Sys.info()[['sysname']],
       Windows = {
            Sys.setenv(RETICULATE_PYTHON="C:\\Users\\sobre\\anaconda3\\envs\\survival\\python.exe")
            #call reticulate
            library(reticulate)
            #activate environment
            use_condaenv("survival", required = TRUE)
       },
       Linux = {
            Sys.setenv(RETICULATE_PYTHON="/home/sobreiro/miniconda3/envs/survival/bin/python")
            library(reticulate)
            use_condaenv("survival", required = TRUE)
       }
)
```

@@

```{r summarytable, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(gtsummary)
library(kableExtra)
library(labelled)

var_label(df_members$year) <- "Inscription year"
var_label(df_members$age) <- "Age in years"
var_label(df_members$sex) <- "Male or female"
var_label(df_members$marital_status) = "Single, married and other."

tbl <- df_members %>%
    tbl_summary(statistic = list(all_continuous() ~ "{mean} ({sd})",
                                 all_categorical() ~ "{p}%"),
                type = list(age ~ "continuous")
               ) %>% add_stat_label()

as_kable_extra(tbl,booktabs=T,caption="Summary statistics of features used")
```

@@

correlation_matrix(df_members, figure_size=(10,10), text_fontsize=6)

r.df_members = df_members

The average age is `r round(mean(df_members$age,na.rm = TRUE),1)` &plusmn;
`r round(sd(df_members$age,na.rm = TRUE),1)`.

total_amount
total_matches
season_matches12%
24%
316 (494)
27 (46)
2.2 (4.1)
months_since_last_payment 19 (32)
dropout
22%
years_membership
11 (11)

```{r test}

str(df_members)
